Technical Report for **Thermal reactionomes reveal divergent responses to thermal

### 2015-10-01 ApTranscriptome_TR.Rmd
tech report to md

---
title: Technical Report for **Thermal reactionomes reveal divergent responses to thermal extremes in warm and cool-climate ant species**
author: [John Stanton-Geddes](john.stantongeddes.research@gmail.com)
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  html_document:
    keep_md: yes
---

@@

mh_plot_sub1 <- qplot(y=Apic, x=Acar, data=md_sub1, fill=value, geom="tile", xlim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-200, 200), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. picea", x = "A. carolinensis") +
  theme(legend.position = "right") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

mh_plot_sub2 <- qplot(y=Acar, x=Apic, data=md_sub2, fill=value, geom="tile", xlim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-200, 200), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. carolinensis", x = "A. picea") + 
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 2.5, ymax = 3.5, fill = "transparent", linetype=2, colour="black")

@@

## Shiny interactive web-app

To assist visualization of specific transcripts, I made a interactive web-app using the [shiny](http://www.rstudio.com/shiny/) package. The scripts for this app are in the sub-directory `.\ApRxN-shinyapp`. The web app is available at https://johnsg.shinyapps.io/ApRxN-shinyapp/

Export data for interactive shiny app.

```{r shiny_file, eval=FALSE, echo=FALSE}
shiny.dt <- TPM.dt.sub[responsive.lms.ann.type[,list(Transcript, best.hit.to.nr, GO.Biological.Process)]]

# scale expression values 
shiny.dt[,TPM.scaled:=scale(TPM), by = Transcript]
str(shiny.dt)
write.csv(shiny.dt, file = "ApRxN-shinyapp/responsive.lms.TPM.csv", quote = TRUE, row.names = FALSE)
```

>>>>

---
title: Technical Report for **Thermal reactionomes reveal divergent responses to thermal
  extremes in warm and cool-climate ant species**
author: '[John Stanton-Geddes](john.stantongeddes.research@gmail.com)'
output:
  html_document:
    keep_md: yes
  pdf_document:
    fig_caption: yes
    includes:
      in_header: header.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc_depth: 2
  word_document: default
---

@@

mh_plot_sub1 <- qplot(y=Apic, x=Acar, data=md_sub1, fill=value, geom="tile", xlim = rev(levels(md_sub1$Acar))) + 
  scale_fill_gradient2(limits=c(-205, 205), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. picea", x = "A. carolinensis") +
  theme(legend.position = "right") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 0.5, ymax = 1.5, fill = "transparent", linetype=2, colour="black")

@@

mh_plot_sub2 <- qplot(y=Acar, x=Apic, data=md_sub2, fill=value, geom="tile", xlim = rev(levels(md_sub2$Apic))) + 
  scale_fill_gradient2(limits=c(-205, 205), low="#f1a340", high="#998ec3") +
  theme(axis.title = element_text(face="italic")) +
  labs(y = "A. carolinensis", x = "A. picea") + 
  theme(legend.position = "none") + 
  geom_rect(xmin = 0.5, xmax = 1.5, ymin = 3.5, ymax = 4.5, fill = "transparent", linetype=2, colour="black") +
  geom_rect(xmin = 1.5, xmax = 2.5, ymin = 2.5, ymax = 3.5, fill = "transparent", linetype=2, colour="black")

@@
